What do incoming university students believe about open science practices in

### 2021-02-09 analysis/Manuscript.Rmd
update preprocessing & data import

#import the data. 
df2 <- read.csv (here::here("data", "students_processed.csv"))
# [[breadcrumbs: work on parsing the columns. It could be that I didn't need to 
# write them as factors in the preprocessing]]
df3 <- read.csv (here::here("data", "students_processed.csv"), 
                 colClasses = c('numeric','factor','factor',
                                rep('character', 3),
                                rep('factor', 2), 'character', 
                                rep('numeric', 35), rep('character', 3),
                                rep('factor', 4), rep('character', 2),
                                rep('factor', 21))
                 )

@@

>>>>

# import the data 
df <- read.csv (here::here("data", "students_processed.csv"))

# convert variables to factors as needed
df$age <- as_factor(df$age)
df$eligibility <- as_factor(df$eligibility)

# convert factors to characters as needed
df$university <- as.character(df$university)
df$degree <- as.character(df$degree)
df$major <- as.character(df$major)
df$major <- as.character(df$major)
df$uni_country <- as.character(df$uni_country)
df$nationality <- as.character(df$nationality)

@@

# note re: eligibility
# only those who say "1" are eligible

df$eligibility <- factor(df$eligibility)
df$eligibility_lab <- factor(df$eligibility_lab)

el <- df %>%
  dplyr::count(eligibility_lab)

# filter(eligibility %in% 1)
